### 2016-11-25 thesis/intro/intro.tex
tmp commit

>>>>

\noindent
Inflammation and immune response, though it may assist in the control of diseases and injuries, have been implicated in the progression of tumour and their acquisition of many of the hallmarks \citep{Hanahan2011}.

There are two pathways of inflammation that contribute to the cancer survival and progression \citep{Mantovani2008}.
The intrinsic pathway is caused by oncogenic characteristics of the cancer cells, where these cells produce inflammatory signals themselves and promote advantageous characteristics for the cancer cells, such as increased proliferation and survival \citep{Mantovani2008}.
On the other hand, the external pathway is caused by infectious or inflammatory conditions in the tumour microenvironment that surround the tumour and assist in the growth of the tumour \citep{Mantovani2008}.
There are two key transcription factors that connect the two pathways of inflammation that ultimately leads to the prommotion  of many, if not all, of the hallmarks discussed so far: \gls{nfkb} and \gls{stat3} \citep{Mantovani2008}.

The study by \citep{Pikarsky2004} showed that \gls{nfkb} was an essential component for the progression of hepatocellular carcinoma, providing the first evidence as to how inflammation may affect the tumour biology.
\gls{nfkb} regulates the expression of genes that encode the inflammatory cytokines, angiogenic factors, and many others, including anti-apoptotic genes (through the activation of \gls{stat3}) \citep{Elinav2013,Mantovani2008}.
\gls{stat3} is a transcription factor that is activated through variety of receptors and pathways, including the \gls{il6} receptor, \glspl{gpcr} and \glspl{tlr} \citep{Yu2007,Yu2014}.
By increasing the transcription of anti-apoptotic proteins such as \gls{bcl2}, \gls{stat3} promotes tumour survival and proliferation \citep{Yu2007}.
Furthermore, \gls{stat3} is able to increase the expression of inflammatory cytokines (such as \gls{il6} and \acrshort{il10}) and \acrshort{vegf}, which provides a positive feedback mechanism for further inflammation (and therefore survival and proliferation signals), and advancement of angiogenesis, respectively \citep{Yu2007}.

Though helpful at times, inflammation induced by the immune system must be taken care of and controlled in order to prevent rapid tumour development and progression.
